\chapter*{Preface}

\addcontentsline{toc}{chapter}{Preface}

This report contains the results of the development of CombinaTorch, which is performed as a master thesis project to fulfill the graduation requirements of the Software Technology MSc at the Delft University of Technology. The process lasted from August 2020 until November 2021. The project has been performed at the Web Information Systems (WIS) research group.\\

This small section is the final piece of my education at TU Delft. The months spent on my thesis were in no small part complicated by the Covid crisis which is hopefully close to conclusion as well. This project came to me after a previous thesis project was shut down at 6 months in, due to corona related complications. However, I am glad to have quickly been handed this opportunity to more freely investigate the field of audio recognition and I hope I can provide aid to future expansion of multi-task research. While its predecessor was more narrowly defined, I had a more open playfield to decide the direction of this project. This project evolved a lot over time and faced a huge amount of difficulties, out of which I hope I can contribute a genuine contribution to developing potential.\\

It hasn't been easy, but I can only thank my supervisor Gerd Kortuem and Alessandro Bozzon for their support and guidance. Especially during the isolating periods which were the hardest, they demonstrated genuine care and insightful feedback, not only for the end result but the process of creating it as well.\\

Finally I would like to give my love and gratitude to my mom Gisele, my dad Jan and my sister Anouk for putting up with me during this time. Also I would like to extend this immense gratitude to my extended family in Delft at the GSC, the small community that helped me survive and work through the heaviest parts of the crisis.\\